A comparison of two second order traffic flow models

### 2015-03-13 FirstDraftMaterials/Draft.tex
Edited draft

\section{Conclusion}
By studying the examples of the LWR, PW and AR models for traffic flow, we see that higher order models are not always more accurate than first order models.  Additionally, the assumptions made in developing higher order relations must conform to the phenomena they are designed to model.  For example, using equations for isotropic fluids to model anisotropic cars in the PW model produces nonphysical results.  The AR model corrects this problem by using a convective derivative rather than a space derivative for the anticipation factor.  Furthermore, the authors verified that their model behaved reasonably by checking it against a list of important conditions.  Therefore, whenever we introduce higher order models, we should follow the example of Aw and Rascle by validating the model's results in a systematic way.

>>>>

\section{Conclusion}
By studying the examples of the LWR, PW and AR models for traffic flow, we see that higher order models are not always more accurate than first order models.  Additionally, the assumptions made in developing higher order relations must conform to the phenomena they are designed to model.  For example, using equations for isotropic fluids to model anisotropic cars in the PW model produces nonphysical results.  The AR model corrects this problem by using a convective derivative rather than a space derivative for the anticipation factor.  Furthermore, the authors verified that their model behaved reasonably by checking it against a list of important conditions for traffic flow.  As illustrated in the analysis of each model and the results that they produce, we see that that the AR model is more successful in modeling realistic traffic flow than the PW model. Therefore, whenever we introduce higher order relations, we should follow the example of Aw and Rascle by validating the model's results in a systematic way.
